---
title: "EDA Report"
author: "Provided by Quantico"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: yes
    toc_depth: 2
    fig_caption: yes
    number_sections: no
classoption: landscape
---

```{r Environment, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
temp <- globalenv()
TempNames <- names(temp)
for(nam in TempNames) {
  assign(x = nam, value = eval(temp[[nam]]), envir = .GlobalEnv)
}
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Yusei+Magic&display=swap');

* {
  box-sizing: border-box;
}

body {
  padding: 0;
  margin: 0;
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-size: 16px;
  line-height: 1.5;
  color: #000000;
  background: linear-gradient(180deg, #787989, #b7b8cf);
}

a {
  color: #b1c5d8;
  text-decoration: none;
}
a:hover {
  text-decoration: underline;
}

.page-header {
  color: #fff;
  text-align: center;
  background-color: #000121;
  background-image: linear-gradient(120deg,#000121,#696b76);
  padding: 1.5rem 2rem;
}
.page-header :last-child {
  margin-bottom: 0.5rem;
}
@media screen and (max-width: 42em) {
  .page-header {
    padding: 1rem 1rem;
  }
}

.project-name {
  margin-top: 0;
  margin-bottom: 0.1rem;
  font-size: 2rem;
}
@media screen and (max-width: 42em) {
  .project-name {
    font-size: 1.75rem;
  }
}

.project-tagline {
  margin-bottom: 2rem;
  font-weight: normal;
  opacity: 0.7;
  font-size: 1.5rem;
}
@media screen and (max-width: 42em) {
  .project-tagline {
    font-size: 1.2rem;
  }
}

.project-author, .project-date {
  font-weight: normal;
  opacity: 0.7;
  font-size: 1.2rem;
}
@media screen and (max-width: 42em) {
  .project-author, .project-date {
    font-size: 1rem;
  }
}

.main-content, .toc {
  max-width: 95%;
  padding: 2rem 4rem;
  margin: 0 auto;
  font-size: 1.1rem;
}

.toc {
  padding-bottom: 0;
}
.toc .toc-box {
  padding: 55px;
  background: linear-gradient(90deg, #000121, #696b76);
  border: solid 1px #000000;
  border-radius: 70px;
  color: white;
  box-shadow: 8px 5px 10px 0px #000000;
}
.toc .toc-box .toc-title {
  margin: 0 0 0.5rem;
  text-align: center;
}
.toc .toc-box > ul {
  margin: 0;
  padding-left: 1.5rem;
}
@media screen and (min-width: 42em) and (max-width: 64em) {
  .toc {
    padding: 2rem 2rem 0;
  }
}
@media screen and (max-width: 42em) {
  .toc {
    padding: 2rem 1rem 0;
    font-size: 1rem;
  }
}

.main-content :first-child {
  margin-top: 0;
}
@media screen and (min-width: 42em) and (max-width: 64em) {
  .main-content {
    padding: 2rem;
  }
}
@media screen and (max-width: 42em) {
  .main-content {
    padding: 2rem 1rem;
    font-size: 1rem;
  }
}
.main-content img {
  max-width: 100%;
}

.main-content h1  {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: bold;
  color: #070e56;
}

.main-content h2 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #121e94;
}
.main-content h3 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #3745d1;
}
.main-content h4 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #374995;
}
.main-content h5 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #000000;
}
.main-content h6 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #000000;
}

.main-content p {
  margin-bottom: 1em;
}
.main-content code {
  padding: 2px 4px;
  font-family: Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: #2c2c2d;
  background-color: #f3f6fa;
  border-radius: 0.3rem;
}
.main-content pre {
  padding: 0.8rem;
  margin-top: 0;
  margin-bottom: 1rem;
  font: 1rem Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: #2c2c2d;
  word-wrap: normal;
  background-color: #e9edf9c9;
  border: solid 1px #001a35;
  border-radius: 0.3rem;
  line-height: 1.45;
  overflow: auto;
}
@media screen and (max-width: 42em) {
  .main-content pre {
    font-size: 0.9rem;
  }
}
.main-content pre > code {
  padding: 0;
  margin: 0;
  color: #2c2c2d;
  word-break: normal;
  white-space: pre;
  background: transparent;
  border: 0;
}
@media screen and (max-width: 42em) {
  .main-content pre > code {
    font-size: 0.9rem;
  }
}
.main-content pre code,
.main-content pre tt {
  display: inline;
  max-width: initial;
  padding: 0;
  margin: 0;
  overflow: initial;
  line-height: inherit;
  word-wrap: normal;
  background-color: transparent;
  border: 0;
}
.main-content pre code:before, .main-content pre code:after,
.main-content pre tt:before,
.main-content pre tt:after {
  content: normal;
}
.main-content ul,
.main-content ol {
  margin-top: 0;
}
.main-content blockquote {
  padding: 0 1rem;
  margin-left: 0;
  color: #2c2c2d;
  border-left: 0.3rem solid #dce6f0;
  font-size: 1.2rem;
}
.main-content blockquote > :first-child {
  margin-top: 0;
}
.main-content blockquote > :last-child {
  margin-bottom: 0;
}
@media screen and (max-width: 42em) {
  .main-content blockquote {
    font-size: 1.1rem;
  }
}
.main-content table {
  width: 100%;
  overflow: auto;
  word-break: normal;
  word-break: keep-all;
  -webkit-overflow-scrolling: touch;
  border-collapse: collapse;
  border-spacing: 0;
  margin: 1rem 0;
}
.main-content table th {
  font-weight: bold;
  background-color: #159957;
  color: #fff;
}
.main-content table th,
.main-content table td {
  padding: 0.5rem 1rem;
  border-bottom: 1px solid #e9ebec;
  text-align: left;
}
.main-content table tr:nth-child(odd) {
  background-color: #f2f2f2;
}
.main-content dl {
  padding: 0;
}
.main-content dl dt {
  padding: 0;
  margin-top: 1rem;
  font-size: 1rem;
  font-weight: bold;
}
.main-content dl dd {
  padding: 0;
  margin-bottom: 1rem;
}
.main-content hr {
  height: 2px;
  padding: 0;
  margin: 1rem 0;
  background-color: #eff0f1;
  border: 0;
}
```

```{r ModelObject_DataSets_And_MetaData, echo = FALSE}
DescribeData <- data.table::data.table(`Variable Name` = names(data))
x <- c(); for(i in names(data)) x <- c(x, class(data[[i]])[1L])
DescribeData[, `Variable Type` := x]
x <- c(); for(i in names(data)) x <- c(x, length(which(is.null(data[[i]]))))
DescribeData[, `NULL Counts` := x]
x <- c(); for(i in names(data)) x <- c(x, length(which(is.na(data[[i]]))))
DescribeData[, `NA Counts` := x]
DescribeData[, `First 5 Values` := "a"]
for(i in seq_along(names(data))) {
  g <- paste0(data[[names(data)[i]]][1L:5L], collapse = ", ")
  data.table::set(DescribeData, i = i, j = "First 5 Values", value = g)
}

# Describe Data
Describe_Data <- reactable::reactable(
  data = DescribeData,
  compact = TRUE,
  defaultPageSize = 10,
  wrap = TRUE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  selection = "multiple",
  showPagination = TRUE,
  showSortable = TRUE,
  showSortIcon = TRUE,
  sortable = TRUE,
  striped = TRUE,
  theme = reactable::reactableTheme(
    color = "black",
    backgroundColor = "#4f4f4f26",
    borderColor = "#dfe2e5",
    stripedColor = "#4f4f4f8f",
    highlightColor = "#8989898f",
    cellPadding = "8px 12px",
    style = list(
      fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
    ),
    searchInputStyle = list(width = "100%")
  )
)

# Create a sampled dataset to speed up computations
if(data[,.N] > 100000L) {
  data1 <- data[order(runif(.N))][seq_len(100000L)]
}

# Full Data
x <- c(); for(i in names(data)) if(class(data[[i]])[1L] %in% c("numeric","integer")) x <- c(x, i)
UnivariateStats <- data.table::data.table(Variables = x)
x <- c(); for(i in names(data)) if(class(data[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data[, min(get(i), na.rm = TRUE)])
UnivariateStats[, Min := round(x,2)]
x <- c(); for(i in names(data)) if(class(data[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data[, max(get(i), na.rm = TRUE)])
UnivariateStats[, Max := round(x,2)]

# Sampled data
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, mean(get(i), na.rm = TRUE)])
UnivariateStats[, Mean := round(x, 2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, median(get(i), na.rm = TRUE)])
UnivariateStats[, Median := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, sd(get(i), na.rm = TRUE)])
UnivariateStats[, `Standard Deviation` := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, e1071::skewness(get(i), na.rm = TRUE)])
UnivariateStats[, Skewness := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, e1071::kurtosis(get(i), na.rm = TRUE)])
UnivariateStats[, Kurtosis := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, sd(get(i), na.rm = TRUE) / mean(get(i), na.rm = TRUE)])
UnivariateStats[, `Coef of Variation` := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, quantile(get(i), probs = 0.01, na.rm = TRUE)])
UnivariateStats[, q01 := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, quantile(get(i), probs = 0.05, na.rm = TRUE)])
UnivariateStats[, q05 := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, quantile(get(i), probs = 0.10, na.rm = TRUE)])
UnivariateStats[, q10 := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, quantile(get(i), probs = 0.25, na.rm = TRUE)])
UnivariateStats[, q25 := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, quantile(get(i), probs = 0.75, na.rm = TRUE)])
UnivariateStats[, q75 := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, quantile(get(i), probs = 0.90, na.rm = TRUE)])
UnivariateStats[, q90 := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, quantile(get(i), probs = 0.95, na.rm = TRUE)])
UnivariateStats[, q95 := round(x,2)]
x <- c(); for(i in names(data1)) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, data1[, quantile(get(i), probs = 0.99, na.rm = TRUE)])
UnivariateStats[, q99 := round(x,2)]

# Describe Data
Univariate_Stats <- reactable::reactable(
  data = UnivariateStats,
  compact = TRUE,
  defaultPageSize = 10,
  wrap = TRUE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  selection = "multiple",
  showPagination = TRUE,
  showSortable = TRUE,
  showSortIcon = TRUE,
  sortable = TRUE,
  striped = TRUE,
  theme = reactable::reactableTheme(
    color = "black",
    backgroundColor = "#4f4f4f26",
    borderColor = "#dfe2e5",
    stripedColor = "#4f4f4f8f",
    highlightColor = "#8989898f",
    cellPadding = "8px 12px",
    style = list(
      fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
    ),
    searchInputStyle = list(width = "100%")
  )
)

# Box Plots
UnivariatePlotList <- list()
for(i in UnivariateVars) {
  if(class(data1[[i]])[1L] %in% c("numeric","integer")) {
    UnivariatePlotList[[i]] <- AutoPlots::Plot.Box(
      dt = data1,
      SampleSize = 100000L,
      XVar = TrendGroupVar,
      YVar = i,
      GroupVar = NULL,
      YVarTrans = "Identity",
      XVarTrans = "Identity",
      FacetRows = 1,
      FacetCols = 1,
      FacetLevels = NULL,
      Height = "600px",
      Width = "975px",
      Title = "Box Plot",
      ShowLabels = FALSE,
      Title.YAxis = i,
      Title.XAxis = NULL,
      EchartsTheme = "wef",
      TimeLine = FALSE,
      
      
      TextColor = "white",
      title.fontSize = 22,
      title.fontWeight = "bold",
      title.textShadowColor = "#63aeff",
      title.textShadowBlur = 3,
      title.textShadowOffsetY = 1,
      title.textShadowOffsetX = -1,
      xaxis.fontSize = 14,
      yaxis.fontSize = 14,
      xaxis.rotate = 0,
      yaxis.rotate = 0,
      ContainLabel = TRUE,
      Debug = FALSE)
  }
}

# Bar Plots
UnivariateCharacterPlotList <- list()
for(i in UnivariateVars) {# i = UnivariateVars[1]
  if(class(data1[[i]])[1L] %in% c("factor","character")) {
    data2 <- data1[, list(Counts = .N), by = c(i)]
    UnivariateCharacterPlotList[[i]] <- AutoPlots::Plot.Bar(
      dt = data2,
      PreAgg = TRUE,
      XVar = i,
      YVar = "Counts",
      GroupVar = NULL,
      LabelValues = NULL,
      YVarTrans = "Identity",
      XVarTrans = "Identity",
      FacetRows = 1,
      FacetCols = 1,
      FacetLevels = NULL,
      AggMethod = "count",
      Height = "600px",
      Width = "975px",
      Title = "Bar Plot",
      ShowLabels = FALSE,
      Title.YAxis = NULL,
      Title.XAxis = NULL,
      EchartsTheme = "wef",
      TimeLine = TRUE,
      
      
      TextColor = "white",
      title.fontSize = 22,
      title.fontWeight = "bold",
      title.textShadowColor = "#63aeff",
      title.textShadowBlur = 3,
      title.textShadowOffsetY = 1,
      title.textShadowOffsetX = -1,
      xaxis.fontSize = 14,
      yaxis.fontSize = 14,
      xaxis.rotate = 0,
      yaxis.rotate = 0,
      ContainLabel = TRUE,
      Debug = FALSE)
  }
}


# Correlation Stats / Plots
x <- c(); for(i in CorrVars) if(class(data1[[i]])[1L] %in% c("numeric","integer")) x <- c(x, i)
if(length(x) > 0L) {
  CorrelogramPlot <- AutoPlots::Plot.CorrMatrix(
    dt = data1,
    CorrVars = x,
    CorrVarTrans = "Identity",
    FacetRows = 1,
    FacetCols = 1,
    FacetLevels = NULL,
    Method = "spearman",
    PreAgg = FALSE,
    Height = "600px",
    Width = "975px",
    Title = "Correlation Matrix",
    ShowLabels = FALSE,
    Title.YAxis = NULL,
    Title.XAxis = NULL,
    EchartsTheme = "wef",
    
    
    TextColor = "white",
    title.fontSize = 22,
    title.fontWeight = "bold",
    title.textShadowColor = "#63aeff",
    title.textShadowBlur = 3,
    title.textShadowOffsetY = 1,
    title.textShadowOffsetX = -1,
    yaxis.fontSize = 14,
    xaxis.fontSize = 14,
    Debug = FALSE)
}

# Trend Stats / Plots
TrendPlotList <- list()
if(length(TrendDateVar) > 0L) {
  x <- c(); for(i in TrendVars) if(class(data[[i]])[1L] %in% c("numeric","integer")) x <- c(x, i)
  if(length(x) > 0L) {
    for(i in x) {
      TrendPlotList[[i]] <- AutoPlots::Plot.Line(
        dt = data,
        AggMethod = "mean",
        PreAgg = FALSE,
        XVar = TrendDateVar,
        YVar = i,
        DualYVar = NULL,
        GroupVar = TrendGroupVar,
        YVarTrans = "Identity",
        DualYVarTrans = "Identity",
        XVarTrans = "Identity",
        FacetRows = 1,
        FacetCols = 1,
        FacetLevels = NULL,
        Height = "600px",
        Width = "975px",
        Title = "Line Plot",
        ShowLabels = FALSE,
        Title.YAxis = NULL,
        Title.XAxis = NULL,
        EchartsTheme = "wef",
        
        
        TimeLine = TRUE,
        Area = FALSE,
        Alpha = 0.5,
        Smooth = TRUE,
        ShowSymbol = FALSE,
        TextColor = "white",
        title.fontSize = 22,
        title.fontWeight = "bold",
        title.textShadowColor = "#63aeff",
        title.textShadowBlur = 3,
        title.textShadowOffsetY = 1,
        title.textShadowOffsetX = -1,
        xaxis.fontSize = 14,
        yaxis.fontSize = 14,
        xaxis.rotate = 0,
        yaxis.rotate = 0,
        ContainLabel = TRUE,
        DarkMode = FALSE,
        Debug = FALSE)
    }
  }
}

```

# <font size="6">EDA Report Descriptions:</font>

The two main goals with this document are to provide a wide range of output to investigate data sets, and to deliver a high quality report design layout to increase user experience. The output provided are intended to be semi-comprehensive. One can always dig deeper into results to gain further insights. In light of that, the results are intended to provide information that one can come to a reasonable conclusion about their data or to find the areas where they need to dig a little deeper.

## Data Description
This section contains a brief overview of your data. The output table includes the variables in the dataset, the data type attribute, a count of NULL values and NA values for each variable, and a list of the first five values for each variable.

## Univariate Statistics
This section contains a table with all the numeric variables in your dataset along with corresponding statistics about each one. The statists include min, max, mean, median, standard deviation, skew, kurtosis, coefficient of variation and a range of percentile values.

## Univariate Plots
This section displays box plots for each univariate variable included. The user can get a better understanding of central tendancy and outliers for each numeric variable. The bar plots for categorical variables show the user counts by each categorical variable level.

## Correlation Analysis
This section displays a correlogram plot of all the numeric variables in your dataset. Spearman correlation is utilized.

## Trend Analysis
This section is a series of time series plots for each numeric variable in your dataset.



#  <font size="5">Describe Data</font>

<details><summary>Expand</summary>
<p>

```{r Model_Evaluation_Metrics, echo=FALSE}
if(!is.null(Describe_Data)) {
  eval(Describe_Data)
}
```

</details>
</p>


#  <font size="5">Univariate Statistics</font>
<p>

<details><summary>Expand</summary>
<p>

```{r Univariate_Stats, echo=FALSE}
if(!is.null(Univariate_Stats)) {
  eval(Univariate_Stats)
} else {
  print("No univariate variables were selected")
}
```

</details>
</p>



#  <font size="5">Univariate Plots</font>

<details><summary>Expand</summary>
<p>


```{r UnivariatePlotList, echo=FALSE}
if(length(UnivariatePlotList) > 0L) {
  echarts4r::e_arrange(UnivariatePlotList)
} else {
  print('No univariate variables were selected')
}
```

</details>
</p>


#  <font size="5">Univariate Bar Plots</font>

<details><summary>Expand</summary>
<p>
```{r UnivariateCharacterPlotList, echo=FALSE}
if(length(UnivariateCharacterPlotList) > 0L) {
  echarts4r::e_arrange(UnivariateCharacterPlotList)
} else {
  print('No univariate variables were selected')
}
```

</details>
</p>



#  <font size="5">Correlation Analysis</font>

<details><summary>Expand</summary>
<p>

```{r CorrelogramPlot, echo=FALSE}
if(length(CorrelogramPlot) > 0L) {
  eval(CorrelogramPlot)
} else {
  print('No correlation variables were selected')
}
```

</details>
</p>

#  <font size="5">Trend Analysis</font>

<details><summary>Expand</summary>
<p>

```{r TrendPlotList, echo=FALSE}
if(length(TrendPlotList) > 0L) {
  echarts4r::e_arrange(TrendPlotList)
} else {
  print('No trend variables were selected')
}
```

<details><summary>Expand</summary>
<p>

```{js, echo=FALSE}
setTimeout(function() {
  var codes = document.querySelectorAll('.dataTables_wrapper');
  var code, i, d, s, p;
  for (i = 0; i < codes.length; i++) {
    code = codes[i];
    p = code.parentNode;
    d = document.createElement('details');
    s = document.createElement('summary');
    s.innerText = 'Details';
    // <details><summary>Details</summary></details>
    d.appendChild(s);
    // move the code into <details>
    p.replaceChild(d, code);
    d.appendChild(code);
  }
});
```
