---
title: "Single Series Forecast Report"
author: "Provided by Quantico"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: yes
    toc_depth: 1
    fig_caption: yes
    number_sections: no
classoption: landscape
---

```{r Environment, include=FALSE}
# theme options up top: hpstr, cayman, architect, AutoQuant
knitr::opts_chunk$set(echo = TRUE)
temp <- globalenv()
TempNames <- names(temp)
for(nam in TempNames) {
  assign(x = nam, value = eval(temp[[nam]]), envir = .GlobalEnv)
}
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Yusei+Magic&display=swap');

* {
  box-sizing: border-box;
}

body {
  padding: 0;
  margin: 0;
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-size: 16px;
  line-height: 1.5;
  color: #000000;
  background: linear-gradient(180deg, #787989, #b7b8cf);
}

a {
  color: #b1c5d8;
  text-decoration: none;
}
a:hover {
  text-decoration: underline;
}

.page-header {
  color: #fff;
  text-align: center;
  background-color: #000121;
  background-image: linear-gradient(120deg,#000121,#696b76);
  padding: 1.5rem 2rem;
}
.page-header :last-child {
  margin-bottom: 0.5rem;
}
@media screen and (max-width: 42em) {
  .page-header {
    padding: 1rem 1rem;
  }
}

.project-name {
  margin-top: 0;
  margin-bottom: 0.1rem;
  font-size: 2rem;
}
@media screen and (max-width: 42em) {
  .project-name {
    font-size: 1.75rem;
  }
}

.project-tagline {
  margin-bottom: 2rem;
  font-weight: normal;
  opacity: 0.7;
  font-size: 1.5rem;
}
@media screen and (max-width: 42em) {
  .project-tagline {
    font-size: 1.2rem;
  }
}

.project-author, .project-date {
  font-weight: normal;
  opacity: 0.7;
  font-size: 1.2rem;
}
@media screen and (max-width: 42em) {
  .project-author, .project-date {
    font-size: 1rem;
  }
}

.main-content, .toc {
  max-width: 95%;
  padding: 2rem 4rem;
  margin: 0 auto;
  font-size: 1.1rem;
}

.toc {
  padding-bottom: 0;
}
.toc .toc-box {
  padding: 55px;
  background: linear-gradient(90deg, #000121, #696b76);
  border: solid 1px #000000;
  border-radius: 70px;
  color: white;
  box-shadow: 8px 5px 10px 0px #000000;
}
.toc .toc-box .toc-title {
  margin: 0 0 0.5rem;
  text-align: center;
}
.toc .toc-box > ul {
  margin: 0;
  padding-left: 1.5rem;
}
@media screen and (min-width: 42em) and (max-width: 64em) {
  .toc {
    padding: 2rem 2rem 0;
  }
}
@media screen and (max-width: 42em) {
  .toc {
    padding: 2rem 1rem 0;
    font-size: 1rem;
  }
}

.main-content :first-child {
  margin-top: 0;
}
@media screen and (min-width: 42em) and (max-width: 64em) {
  .main-content {
    padding: 2rem;
  }
}
@media screen and (max-width: 42em) {
  .main-content {
    padding: 2rem 1rem;
    font-size: 1rem;
  }
}
.main-content img {
  max-width: 100%;
}

.main-content h1  {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: bold;
  color: #070e56;
}

.main-content h2 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #121e94;
}
.main-content h3 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #3745d1;
}
.main-content h4 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #374995;
}
.main-content h5 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #000000;
}
.main-content h6 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #000000;
}

.main-content p {
  margin-bottom: 1em;
}
.main-content code {
  padding: 2px 4px;
  font-family: Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: #2c2c2d;
  background-color: #f3f6fa;
  border-radius: 0.3rem;
}
.main-content pre {
  padding: 0.8rem;
  margin-top: 0;
  margin-bottom: 1rem;
  font: 1rem Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: #2c2c2d;
  word-wrap: normal;
  background-color: #e9edf9c9;
  border: solid 1px #001a35;
  border-radius: 0.3rem;
  line-height: 1.45;
  overflow: auto;
}
@media screen and (max-width: 42em) {
  .main-content pre {
    font-size: 0.9rem;
  }
}
.main-content pre > code {
  padding: 0;
  margin: 0;
  color: #2c2c2d;
  word-break: normal;
  white-space: pre;
  background: transparent;
  border: 0;
}
@media screen and (max-width: 42em) {
  .main-content pre > code {
    font-size: 0.9rem;
  }
}
.main-content pre code,
.main-content pre tt {
  display: inline;
  max-width: initial;
  padding: 0;
  margin: 0;
  overflow: initial;
  line-height: inherit;
  word-wrap: normal;
  background-color: transparent;
  border: 0;
}
.main-content pre code:before, .main-content pre code:after,
.main-content pre tt:before,
.main-content pre tt:after {
  content: normal;
}
.main-content ul,
.main-content ol {
  margin-top: 0;
}
.main-content blockquote {
  padding: 0 1rem;
  margin-left: 0;
  color: #2c2c2d;
  border-left: 0.3rem solid #dce6f0;
  font-size: 1.2rem;
}
.main-content blockquote > :first-child {
  margin-top: 0;
}
.main-content blockquote > :last-child {
  margin-bottom: 0;
}
@media screen and (max-width: 42em) {
  .main-content blockquote {
    font-size: 1.1rem;
  }
}
.main-content table {
  width: 100%;
  overflow: auto;
  word-break: normal;
  word-break: keep-all;
  -webkit-overflow-scrolling: touch;
  border-collapse: collapse;
  border-spacing: 0;
  margin: 1rem 0;
}
.main-content table th {
  font-weight: bold;
  background-color: #159957;
  color: #fff;
}
.main-content table th,
.main-content table td {
  padding: 0.5rem 1rem;
  border-bottom: 1px solid #e9ebec;
  text-align: left;
}
.main-content table tr:nth-child(odd) {
  background-color: #f2f2f2;
}
.main-content dl {
  padding: 0;
}
.main-content dl dt {
  padding: 0;
  margin-top: 1rem;
  font-size: 1rem;
  font-weight: bold;
}
.main-content dl dd {
  padding: 0;
  margin-bottom: 1rem;
}
.main-content hr {
  height: 2px;
  padding: 0;
  margin: 1rem 0;
  background-color: #eff0f1;
  border: 0;
}
```

```{r FC_Objects 1, echo = FALSE}
if(GridTune_proc) {
  
  # @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@ ----
  # Grid Tuning Output                                                        ----
  # @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@ ----

  # Evaluation Metrics ----
  Experiment_Grid <- reactable::reactable(
    data = DataList[[EG]]$data,
    compact = TRUE,
    defaultPageSize = 10,
    wrap = TRUE,
    filterable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    searchable = TRUE,
    selection = "multiple",
    showPagination = TRUE,
    showSortable = TRUE,
    showSortIcon = TRUE,
    sortable = TRUE,
    striped = TRUE,
    theme = reactable::reactableTheme(
      color = "black",
      backgroundColor = "#4f4f4f26",
      borderColor = "#dfe2e5",
      stripedColor = "#4f4f4f8f",
      highlightColor = "#8989898f",
      cellPadding = "8px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
      ),
      searchInputStyle = list(width = "100%")
    )
  )
} else {
  
  Experiment_Grid <- NULL
  
}

```

```{r FC_Objects 2, echo = FALSE}
  # ----

  # ----

  # @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@ ----
  # Forecasting Output                                                        ----
  # @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@ ----

  # Forecast Data ----
if(Forecast_proc) {
  Forecast_Data <- reactable::reactable(
    data = DataList[[FCD]]$data,
    compact = TRUE,
    defaultPageSize = 10,
    wrap = TRUE,
    filterable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    searchable = TRUE,
    selection = "multiple",
    showPagination = TRUE,
    showSortable = TRUE,
    showSortIcon = TRUE,
    sortable = TRUE,
    striped = TRUE,
    theme = reactable::reactableTheme(
      color = "black",
      backgroundColor = "#4f4f4f26",
      borderColor = "#dfe2e5",
      stripedColor = "#4f4f4f8f",
      highlightColor = "#8989898f",
      cellPadding = "8px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
      ),
      searchInputStyle = list(width = "100%")
    )
  )
  
} else {
  
  Forecast_Data <- NULL
  
}

```


# <font size="6">Forecasting Report Description:</font>

The Single Series Forecasting Report is pretty simple. There are two run modes for utilizing these models: grid tuning and forecasting.

The grid tuning results is a table of parameters and performance metrics to help you understand which parameters led to the best forecast results.

The forecast mode is what you run to generate the forecast. The forecast results is a table of the historical data, the forecast data, and prediction interval data. On top of that, a plot is rendered to display the historical, forecast, and prediction interval data.

<br>

# <font size="6">Grid Tuning</font>

```{r Experiment_Grid, echo=FALSE}
if(!is.null(Experiment_Grid)) {
  eval(Experiment_Grid)
}
```

<br>

# <font size="6">Forecasting</font>

```{r Forecast_Data, echo = FALSE}
if(length(Forecast_Data) > 0) {
  eval(Forecast_Data)
}
```

<br>

```{r Forecast_Plot, echo = FALSE}
if(length(Forecast_Plot) > 0) {
  eval(Forecast_Plot)
}
```
